\textbf{Matching the forecast horizon with the relevant spatial and temporal processes and data sources}

### 2020-06-08 doc/response_2_reviews_Ecography2.txt

Recommendation by the Subject Editor (anonymous):

Both reviewers found the manuscript to be much improved from the previous version, I fully agree with them. While reviewer 1 has only minor comments, reviewer 2 still has some more major concerns that need to be addressed. Thus I invite you to prepare a revision which implements those suggestions.

RESPONSE: We thank the Editor for the opportunity to address the reviewers' concerns with another revision/

@@

Reviewer(s)' Comments to Author:
Reviewer: 1

Comments to the Author
The manuscript has improved since its previous round. The work is interesting and carefully executed even though authors should be a bit more critical on the generality of their results. After all this is a very theoretical study where the simulation model is rather simplistic description of the reality.

RESPONSE: We re-read the Discussion to make sure we are not over-selling our results. We believe it is clear that our results are based only on simulations of a couple theoretical models, and that empirical tests are still required. Furthermore, the text is littered with qualifying words such as "may", "likely", and "suggest."

@@

Reviewer: 2

Comments to the Author
I reviewed this previously, and asked that more details be included about the methods. Whilst there is some improvement, it is still not up to the standard I would hope for. For example, the text still does not say which years are used in the estimation. It is now clear that only a single simulation is used, which is not really acceptable. We need to be shown (not just told) that the results replicate. being able to replicate the simulations and analysis would also make it easier to run the models under different conditions. This would enable the exploration of a wider range of conditions, which should help to explain the main results.

I would recommend finding a single statistic that can be used to summarise the predictive success, e.g. the probability of the data given the predictions. This can be calculated across some or all of the sites (rather than having to chose a single site to look at). So, for a single simulation, data can be taken at time t, with spatial data across the whole region, and the same amount of temporal data (from either one or several sites). The predictions can be compared to the "real" data at (say) 10 or 1000 years into the future. This basic set-up can be replicated repeatedly under different scenarios, e.g. no climate change, climate change before the sampling, climate change after the sampling, etc.

RESPONSE: We agree that "showing" is better than "telling." We chose not to take the reviewer's suggestion of finding a single measure of model accuracy, because we want readers to focus on the most important general result, which is the shift in model weight from time-series to space-for-time with increasing forecast time scale. We have added a new supplementary figure (SI Fig. 1) showing the temporal trend in the model weight term for 10 independent realizations of the community tunover example and the eco-evolutionary example. We believe this figure shows how consistent the pattern is across simulation runs.

@@

One issue that I think needs to be addressed is the problem of extrapolation outside of the environmental conditions when the sampling is done. In practice, this is a major concern. If, say, methods work well until they extrapolate, then that would be an important message for studies of real organisms.

RESPONSE: We added text to the discussion to flag the important issue of extrapolation. The third to last discussion paragraph now reads as follow, where \comments{} show the new text. 
"The idea of combining forecasts with model weights and allowing the weights to shift across the forecast horizon need not be limited to \comment{extremely simple statistical models like the ones we used in this study}. The same concept could work for any class of models that differ in predictive skill at different forecast horizons, \comment{such as more sophisticated phenomenological models designed to minimize problems of extrapolating outside the historical range of variation, or a set of process-based models focusing on mechanisms operating at different time scales.}  Determining the model weights \emph{a priori} might be easier when models feature explicit processes with characteristic time scales."
We note that the extrapolation issue is also addressed in the Introduction (lines 132-135).

### 2020-06-08 doc/manuscript.tex
finished response

Space-for-time modeling approaches for predicting long-term, steady-state outcomes of ecological change have also been tested empirically, primarily via hind-casting. Overall, the results are mixed: some tests show reasonable prediction of changes in community composition \citep{Blois2013,Illan2014} or species distributions \citep{Norberg2019}, supporting the hypothesis that datasets spanning spatial gradients capture the long-term outcome of interactions between fast processes and slower processes such as ecological and evolutionary selection, dispersal, and responses to large changes in the environment. Other attempts to validate predictions from space-for-time models have been discouraging \citep{Worth2014,Illan2014,Davis2014,Brun2016,Veloz2012}, indicating violations of model assumptions or effects of transient dynamics. However, predictions from the space-for-time approaches are rarely compared directly to predictions from time-series models (\citealt{harris_forecasting_2018} but see \citealt{Renwick2018}). We need more such comparisons to identify the appropriate modeling approach for different forecast horizons.

@@

The idea of combining forecasts with model weights and allowing the weights to shift across the forecast horizon need not be limited to \comment{extremely simple statistical models like the ones we used in this study}. The same concept could work for any class of models that differ in predictive skill at different forecast horizons. \comment{One possibility might be more sophisticated phenomenological models designed to minimize problems of extrapolating outside the historical range of variation. A set of process-based models focusing on processes operating at different time scales would be another.}  Determining the model weights \emph{a priori} might be easier when models feature explicit processes with characteristic time scales.

>>>>

Space-for-time modeling approaches for predicting long-term, steady-state outcomes of ecological change have also been tested empirically, primarily via hindcasting. Overall, the results are mixed: some tests show reasonable prediction of changes in community composition \citep{Blois2013,Illan2014} or species distributions \citep{Norberg2019}, supporting the hypothesis that datasets spanning spatial gradients capture the long-term outcome of interactions between fast processes and slower processes such as ecological and evolutionary selection, dispersal, and responses to large changes in the environment. Other attempts to validate predictions from space-for-time models have been discouraging \citep{Worth2014,Illan2014,Davis2014,Brun2016,Veloz2012}, indicating violations of model assumptions or effects of transient dynamics. However, predictions from the space-for-time approaches are rarely compared directly to predictions from time-series models (\citealt{harris_forecasting_2018}, but see \citealt{Renwick2018}). We need more such comparisons to identify the appropriate modeling approach for different forecast horizons.

@@

The idea of combining forecasts with model weights and allowing the weights to shift across the forecast horizon need not be limited to \comment{extremely simple statistical models like the ones we used in this study}. The same concept could work for any class of models that differ in predictive skill at different forecast horizons, \comment{such as more sophisticated phenomenological models designed to minimize problems of extrapolating outside the historical range of variation, or a set of process-based models focusing on mechanisms operating at different time scales.}  Determining the model weights \emph{a priori} might be easier when models feature explicit processes with characteristic time scales.
